Lab 2 Final Report: COVID-19 Case Rate vs Population Demographics and Mask Policy

### 2020-12-07 Jackson_Liu_Temlock_Zhang_Lab2_Draft_Report.Rmd
Added identical distribution information.

>>>>

The identical distribution of states as individual samples in the model is also questionable. Similar to how connections or commonalities between states make them less than truly independent, certain factors would also influence the distribution so that some states are representative of a different underlying distribution than one another. For example, if one geographic region as a whole has a factor which influences the spread of the virus differently than another, multiple underlying distributions may be present in the sample. If still a new geographic region with many states was added to the sample, and the measures of central tendency of the data continued to evolve, there would be a further indication that the underlying distribution is not identical. Without a possibility of refining the data sample however, as states would be immutable in this regard, the assumption must be made for any potential analysis.
